SVG: The Paper

### 2022-04-13 Analysis/index.Rmd
a few minor edits

```{r, echo = TRUE}
qs <- quantile(a_trl$prop_max, c(0.05, 0.95))

trls_hard <- filter(a_trl, prop_max < qs[1]) %>% sample_n(3)
trls_easy <- filter(a_trl, prop_max > qs[2]) %>% sample_n(3)

# 
source("plot_trial.R")

plts <- map(1:3, plot_trial, trls_easy, a, d)

#plts[1] + plts[2] + plts[3]

plot(plot_trial(1, trls_hard, a, d))

```

>>>>

```{r, echo = TRUE}
qs <- quantile(a_trl$prop_max, c(0.05, 0.40, 0.60, 0.95))

trls_hard <- filter(a_trl, prop_max < qs[1]) %>% sample_n(3)
trls_mid  <- filter(a_trl, prop_max > qs[2], prop_max < qs[3]) %>% sample_n(3)
trls_easy <- filter(a_trl, prop_max > qs[4]) %>% sample_n(3)

# 
source("functions/plot_trial.R")
```

```{r fig.cap = "A random selection of *good* trials."}
plts <- map(1:3, plot_trial, trls_easy, a, d)

plts[[1]] + plts[[2]] 
```

Here are some typical trials:

```{r fig.cap = "A random selection of *typical* trials."}
plts <- map(1:3, plot_trial, trls_mid, a, d)

plts[[1]] + plts[[2]] 
```

Now let's look at less predictable trials:

```{r fig.cap = "A random selection of *hard* trials."}
plts <- map(1:3, plot_trial, trls_hard, a, d)

plts[[1]] + plts[[2]] + plts[[3]]
```

# Initial Selection

## QJEP Dataset

```{r}
d <- read_csv("data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
  filter(found == 1) %>%
  mutate(condition = as_factor(condition))

ggplot(d, aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1)) + 
  facet_wrap(~observer)

d %>% group_by(observer, condition) %>% 
  summarise(x = median(x), y = median(y)) %>%
  ggplot(aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1))

plt_x <- ggplot(d, aes(x)) + geom_histogram(bins = 10) 
plt_y <- ggplot(d, aes(y)) + geom_histogram(bins =  8) 
plt_x + plt_y
```

## Tagu dataset

```{r}
d <- read_csv("data/tagu_2020_prox_mouse.csv", show_col_types = FALSE) %>%
  filter(found == 1) %>%
  mutate(condition = as_factor(condition))

ggplot(d, aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
  #coord_cartesian(xlim = c(0, 1), ylim = c(0, 1)) + 
  facet_wrap(~observer)

d %>% group_by(observer, condition) %>% 
  summarise(x = median(x), y = median(y)) %>%
  ggplot(aes(x, y, colour = condition)) + geom_point(alpha = 0.25) #+
#coord_cartesian(xlim = c(0, 1), ylim = c(0, 1))

plt_x <- ggplot(d, aes(x)) + geom_histogram(bins = 10) 
plt_y <- ggplot(d, aes(y)) + geom_histogram(bins =  8) 
plt_x + plt_y
```
